---
title: "Dental Health Inequalities"
author: "NHS England and NHS Improvement"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  powerpoint_presentation
---


```{r include = FALSE}
library(tidyverse)
library(readxl)
source("health_inequalities_functions.R")
monthly_HE <- readRDS("~/R-Projects/SMT-Dental-Report/data/health_inequalities_data/monthly_HE.rds")
child_band2_FV <- readRDS("~/R-Projects/SMT-Dental-Report/data/health_inequalities_data/child_band2_FV.rds")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## National Level

## Band 2 courses of treatment ncompared to FV rates for 3-16 year olds
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_child_band2_FV()
```

## Total FP17s by ethnic group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = total_FP17, band_name = "Total", numOrPerc = "num", level = "National")
```

## Banded FP17s by ethnic group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = band1, band_name = "Band 1", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = band2, band_name = "Band 2", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = band3, band_name = "Band 3", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = urgent, band_name = "Urgent", numOrPerc = "num", level = "National")
```

## Percentage of total FP17s by ethnic group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = perc_total_FP17, band_name = "Total", numOrPerc = "perc", level = "National")
```

## Percentage of banded FP17s by ethnic group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = perc_band1, band_name = "Band 1", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = perc_band2, band_name = "Band 2", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = perc_band3, band_name = "Band 3", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_ethnicity(band = perc_urgent, band_name = "Urgent", numOrPerc = "perc", level = "National")
```



## Total FP17s by gender
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = total_FP17, band_name = "Total", numOrPerc = "num", level = "National")
```

## Banded FP17s by gender
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = band1, band_name = "Band 1", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = band2, band_name = "Band 2", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = band3, band_name = "Band 3", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = urgent, band_name = "Urgent", numOrPerc = "num", level = "National")
```

## Percentage of total FP17s by gender
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = perc_total_FP17, band_name = "Total", numOrPerc = "perc", level = "National")
```

## Percentage of banded FP17s by gender
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = perc_band1, band_name = "Band 1", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = perc_band2, band_name = "Band 2", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = perc_band3, band_name = "Band 3", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_gender(band = perc_urgent, band_name = "Urgent", numOrPerc = "perc", level = "National")
```



## Total FP17s by patient charge status
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = total_FP17, band_name = "Total", numOrPerc = "num", level = "National")
```

## Banded FP17s by patient charge status
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = band1, band_name = "Band 1", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = band2, band_name = "Band 2", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = band3, band_name = "Band 3", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = urgent, band_name = "Urgent", numOrPerc = "num", level = "National")
```

## Percentage of total FP17s by patient charge status
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = perc_total_FP17, band_name = "Total", numOrPerc = "perc", level = "National")
```

## Percentage of banded FP17s by ethnic group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = perc_band1, band_name = "Band 1", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = perc_band2, band_name = "Band 2", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = perc_band3, band_name = "Band 3", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_charge_status(band = perc_urgent, band_name = "Urgent", numOrPerc = "perc", level = "National")
```




## Total FP17s by age group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = total_FP17, band_name = "Total", numOrPerc = "num", level = "National")
```

## Banded FP17s by patient age group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = band1, band_name = "Band 1", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = band2, band_name = "Band 2", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = band3, band_name = "Band 3", numOrPerc = "num", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = urgent, band_name = "Urgent", numOrPerc = "num", level = "National")
```

## Percentage of total FP17s by age group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = perc_total_FP17, band_name = "Total", numOrPerc = "perc", level = "National")
```

## Percentage of banded FP17s by age group
```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = perc_band1, band_name = "Band 1", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = perc_band2, band_name = "Band 2", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = perc_band3, band_name = "Band 3", numOrPerc = "perc", level = "National")
```

```{r echo = FALSE, warning = FALSE, error = FALSE, fig.height=4, fig.width=7}
plot_HE_age(band = perc_urgent, band_name = "Urgent", numOrPerc = "perc", level = "National")
```


## Regional Level

## East of England
## London
## Midlands
## North East and Yorkshire
## North West
## South East
## South West

