---
title: "Dental Data Pack"
subtitle: "`r params$region_STP_name`"
author: "`r format(Sys.time(), '%B, %Y')`"
output:
  slidy_presentation: default
  beamer_presentation:
    includes:
      in_header: slide_format2.tex
sansfont: Calibri Light
fontsize: 8pt
classoption: aspectratio = 169
params:
  level: "National"
  region_STP_name: "National"
---

```{r include = FALSE}
library(tidyverse)
library(readxl)
source("../R/SMT_functions.R")
source("../R/format_SMT_data.R")

#load in raw data
UDA_calendar_data <- readRDS("../data/cleaned_data_up_to_october/UDA_calendar_data.rds")
UOA_calendar_data <- readRDS("../data/cleaned_data_up_to_october/UOA_calendar_data.rds")
UDA_scheduled_data <- readRDS("../data/cleaned_data_up_to_october/UDA_scheduled_data.rds")
UOA_scheduled_data <- readRDS("../data/cleaned_data_up_to_october/UOA_scheduled_data.rds")
historical_UDA_scheduled_data <- readRDS("../data/cleaned_data_up_to_september/historical_UDA_scheduled_data.rds")

dental_data_111 <- read_excel("../data/cleaned_data_up_to_october/111_dental_data.xlsx", 
                              col_types = c("date", "text", "text", 
                                            "text", "numeric"))

prototype_contracts <- read_excel("../data/prototype_contracts.xlsx")
contractor_categories <- readRDS("../data/cleaned_data_up_to_october/contractor_categories.RDS")

UDA_delivery <- get_into_slide5_7_format_calendar(STP_lines = T, renameColumns = T)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Contents 

#### Calendar data 2021/2022 (explanation slide 3)
###### April to October data only:
* Monthly UDA delivery of contracted quarterly value against threshold (4 and 5)
* Monthly UOA delivery of contracted quarterly value against threshold (8 and 9)
* N.B. these analyses exclude contracts with annual contracted UDAs of less than 
or equal to 100 and prototype contracts

#### Scheduled data activity slides (explanation slide 3)
* Monthly UDA delivery of contracted annual value scaled up by 12 (6)
* Monthly UOA delivery of contracted annual value scaled up by 12 (10)
* Historic banded Courses of Treatment comparison (12)
* Total urgent FP17 form count across financial years (13)  

*Please Note: Slides 4, 5, 8 and 9 use calendar data as a measure of activity.*
*Slides 6, 7, 10-13 use scheduled data, as per previous SMT data packs.*

## Calendar and scheduled data 
### Calendar data explanation 

* Slides 4, 5, 8 and 9 are based on calendar month data
* Calendar data is based on courses of treatment completed within an entire month, for example 1st February to 28th Feb
* For calendar data, if a COT was completed in February but not declared till March, that activity would still be registered as
occurring in February.
* This means that graphs using calendar data may change for historical months as more COTs are registered. 
* The activity % is now based on total number of UDA/UOAs delivered as a % of total contracted UDA/UOAs per quarter.


### Scheduled data explanation
* Slides 6, 7, 10-13 are based on scheduled data
* The scheduling time period is usually between the 20th of one month and the 20th of the next month i.e., 21st April to the
19th May. That means that any Mandatory contract COT completed after this period will not be included in the May
scheduled data. However, if for example a COT was completed on May 1st, but reported to the BSA after the end of the
reporting period (April 21st – May 19th), that activity would go into the following scheduled period. As a result, the
scheduling period can be considered fixed.
* N.B.Scheduled data for April is from 1st April - 21st April. This has been taken into account when scaling up to annual delivery.

## Number of contracts by MY category
#### Including prototypes and contracts with annual contracted UDA < 100
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
knitr::kable(table_number_cat_contracts(remove_prototypes = F))
```
#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
knitr::kable(table_number_cat_contracts(remove_prototypes = T))
```
* See appendix for list of which type of contracts fall into each category.


## UDA activity data 
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = params$level, region_STP_name = params$region_STP_name)`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (65% for Oct-Dec, 60% for Apr-Sep).
* In **`r format(Sys.Date() - lubridate::weeks(4), "%B")`**, scaled delivery was **62.4%**. This was **below** the 65% threshold.
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3).


## UDA activity data by region
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = T, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```


## UDA activity data by MY Category
#### Prototypes and contracts with annual contracted UDAs < 100 included
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = F,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

## 
#### Prototypes and contracts with annual contracted UDAs < 100 excluded
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```



## UDA cumulative activity data

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_Q3_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = params$level,
                                  region_STP_name = params$region_STP_name)
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(level = params$level, region_STP_name = params$region_STP_name)`** GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (65% for Oct-Dec).
* From October to `r format(Sys.Date() - lubridate::month(1), "%B")` **`r get_Q3_num_contracts_on_target(level = params$level, region_STP_name = params$region_STP_name)`**
contracts (**`r round(get_Q3_num_contracts_on_target(level = params$level, region_STP_name = params$region_STP_name)*100/get_num_contracts(level = params$level, region_STP_name = params$region_STP_name))`%**)
have delivered the required UDAs or more towards the Q3 threshold (65%) by the end of December 2021.


## Scheduled UDA delivery

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = params$level,
                                  region_STP_name = params$region_STP_name)
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.

## UDA delivery profile

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = params$level,
                          region_STP_name = params$region_STP_name)
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.

## UOA activity data

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = params$level, region_STP_name = params$region_STP_name)`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (85% for Oct-Dec, 80% for Apr-Sep).
* In **`r format(Sys.Date() - lubridate::weeks(4), "%B")`**, **69.3%** of the total contracted UOAs for Q3 were delivered. This was **below** the 85% threshold.
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3).


## UOA activity data by region
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = T, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```


## UOA activity data by MY Category
#### Prototypes and contracts with annual contracted UDAs < 100 included
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = F,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

##
#### Prototypes and contracts with annual contracted UDAs < 100 excluded
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```



## UOA cumulative activity data

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_Q3_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = params$level,
                                  region_STP_name = params$region_STP_name)
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = params$level, region_STP_name = params$region_STP_name)`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (85% for Oct-Dec).
* From October to `r format(Sys.Date() - lubridate::month(1), "%B")` **`r get_Q3_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = params$level, region_STP_name = params$region_STP_name)`** contracts (**`r round(get_Q3_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = params$level, region_STP_name = params$region_STP_name)*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = params$level, region_STP_name = params$region_STP_name))`%**) have delivered
the required UOAs or more towards the Q3 threshold (85%) by the end of December 2021.


## UOA delivery

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = params$level,
                                  region_STP_name = params$region_STP_name)
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.

## UOA delivery profile

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = params$level,
                          region_STP_name = params$region_STP_name)
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.

## Time series of banded Courses of Treatment
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = params$level,
                region_STP_name = params$region_STP_name)
```

## Urgent treatment form submissions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height=4}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = params$level,
                region_STP_name = params$region_STP_name)
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in **`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** was
**`r get_num_urgent_forms(level = params$level, region_STP_name = params$region_STP_name)`**, whilst in **`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** this number was
**`r get_num_urgent_forms_2019(level = params$level, region_STP_name = params$region_STP_name)`**, which is a **`r round((get_num_urgent_forms(level = params$level, region_STP_name = params$region_STP_name) - get_num_urgent_forms_2019(level = params$level, region_STP_name = params$region_STP_name)) *100 / get_num_urgent_forms_2019(level = params$level, region_STP_name = params$region_STP_name))`%** change from the pre-COVID
world.


## Appendix
#### MY Category clasification breakdown:
"Cat 1 - Details in CoMPASS Correct"                                             "Cat 2 - Carry Forward - Other"                                                 
"Cat 2 - Flexibly Commissioned Contract"                                         "Cat 2 - Force majeure accepted"                                                
"Cat 2 - Force majeure o/s"                                                      "Cat 2 - In-year incorporation/merge (Parent contract - letter will be sent)"   
"Cat 2 - Incomplete OOH/other access services"                                   "Cat 2 - Late subs processed"                                                   
"Cat 2 - Mixed / CoT Contract"                                                   "Cat 2 - Non-recurring activity"                                                
"Cat 2 - Open in-year"                                                           "Cat 2 - Other"                                                                 
"Cat 2 - Request to re-base"                                                     "Cat 2 - Review Carry Forward"                                                  
"Cat 2 - Sub Contracts (Parent contract - letter will be sent)"                  "Cat 2 - UDA Value below £15.00"                                                
"Cat 2 - UDA Value exceeds £49.99"                                               "Cat 2 - UDC"                                                                   
"Cat 2 - UOA Value exceeds £75.00"                                               "Cat 2 - Closed in-year"                                                       
"Cat 2 - Incomplete service line entries"                                        "Cat 3 - CDS"                                                                   
"Cat 3 - Closed in year"                                                         "Cat 3 - Contract End Date before 01/04/2020"                                   
"Cat 3 - Contract End Date before 01/04/2021"                                    "Cat 3 - Contract End Date before 01/04/2022"                                   
"Cat 3 - DCO req to resolve locally"                                             "Cat 3 - Domiciliary/ Sedation"                                                 
"Cat 3 - IMOS/MOS"                                                               "Cat 3 - In-year incorporation/merge (Child contract - letter will not be sent)"
"Cat 3 - Incomplete OOH/other access services"                                   "Cat 3 - Known performance/contract issues"                                     
"Cat 3 - No Contracted activity"                                                 "Cat 3 - No Contracted value"                                                   
"Cat 3 - Not paid by the NHSBSA"                                                 "Cat 3 - Open in year"                                                          
"Cat 3 - Other"                                                                  "Cat 3 - Other - Please state why"                                              
"Cat 3 - Other Advanced/Additional Services"                                     "Cat 3 - PDS Plus"                                                              
"Cat 3 - Prison"                                                                 "Cat 3 - Sub Contracts (Child contract - letter will not be sent)"              
"Cat 4 - Dental Contract Reform"    

## Appendix 2
#### Data sources: 
* BSA calendar and scheduled UDA data downloaded from the "NHS England Central Dashboard" on eDEN.
This data is downloaded monthly and put on the NCDR. Tables are:
+ [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UDA_calendar]
+ [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UDA_scheduled]
+ [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UOA_calendar]
+ [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UOA_scheduled]
* A list of prototype contracts are also available in:
+ [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[prototype_contracts]
* A table of UDA delivery on STP level is available in:
+ [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UDA_delivery]

* 111 data comes from the pathways tool which is received monthly by email.
