---
title: SMT Dental Data Report 
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: NHS England and Improvement
output:
  beamer_presentation:
    latex_engine: xelatex
sansfont: Calibri Light
fontsize: 9pt
---

```{r include = FALSE}
library(tidyverse)
library(readxl)
source("../R/SMT_functions.R")
source("../R/format_new_data.R")

#load in raw data
UDA_calendar_data <- readRDS("~/R-Projects/SMT-Dental-Report/data/cleaned_data_up_to_august/UDA_calendar_data.rds")
UOA_calendar_data <- readRDS("~/R-Projects/SMT-Dental-Report/data/cleaned_data_up_to_august/UOA_calendar_data.rds")
UDA_scheduled_data <- readRDS("~/R-Projects/SMT-Dental-Report/data/cleaned_data_up_to_august/UDA_scheduled_data.rds")
UOA_scheduled_data <- readRDS("~/R-Projects/SMT-Dental-Report/data/cleaned_data_up_to_august/UOA_scheduled_data.rds")

#load in historic data not available in raw
slide5_UDA_delivery_historic <- readRDS("~/R-Projects/SMT-Dental-Report/data/cleaned_data_up_to_august/slide5_UDA_delivery_historic.rds")
slide7_UOA_delivery_historic <- readRDS("~/R-Projects/SMT-Dental-Report/data/cleaned_data_up_to_august/slide7_UOA_delivery_historic.rds")
slide8_banded_CoT_historic <- readRDS("~/R-Projects/SMT-Dental-Report/data/cleaned_data_up_to_august/slide8_banded_CoT_historic.rds")

prototype_contracts <- read_excel("~/R-Projects/SMT-Dental-Report/data/prototype_contracts.xls")

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Contents 

#### Calendar data 2021/2022 (explanation slide 3)
###### April to September data only:
* UDA contracts achieving 60% (4)
* UOA contracts achieving 80% (6)

#### Scheduled data activity slides (explanation slide 3)
* Total UDA activity scales up by 12 (5)
* Total UOA activity scaled up by 12 (7)
* Historic banded Courses of Treatment comparison (8)
* Total urgent FP17 form count 2019/2020 to 2020/2021 (9)  

*Please Note: Slides 4 and 6 use calendar data as a measure of activity for the first half of the 2021-2022 year.*
*Slides 5, 7 and 8-9 use scheduled data, as per previous SMT data packs.*
*The scheduled data is from 16th June – 16th July and is fixed.*

## Calendar data explanation {data-background="slide-backgrounds\NHS_background.JPG"}

* Slides 4 & 6 are based on calendar month data
* Calendar data is based on courses of treatment completed within an entire month, for example 1st February to 28th Feb
* For calendar data if a COT was completed in February but not declared till March, that activity would still be registered as
occurring in February.
* Calculation has changed from last month- rather than taking an average of all providers percentage activity to date, the activity %
is now based on total number of UDA/Os delivered as a % of the total number of UDA/Os expected by September (60%/80%
threshold).

### Scheduled data explanation
* Slides 5,7, 8 and 9 are based on scheduled data
* The scheduling time period is usually between the 20th of one month and the 20th of the next month i.e., 21st April to the
19th May. That means that any Mandatory contract COT completed after this period will not be included in the May
scheduled data. However, if for example a COT was completed on May 1st, but reported to the BSA after the end of the
reporting period (April 21st – May 19th), that activity would go into the following scheduled period. As a result, the
scheduling period can be considered fixed.


## UDA activity data for 2021/2022
```{r echo = FALSE, warning = FALSE, fig.height=4}
plot_UDA_UOA_to_target(data = UDA_calendar_data, UDAorUOA = "UDA", level = "National")
```

* This chart shows the average monthly performance of
the 6851 GDS/PDS/PDS+ contracts (with annual contracted UDAs
of greater than or equal to 100) measured against the minimum
activity required (16.7%) to reach the 60% threshold by
September. 
* In the month of July 3089 contracts (45%) achieved at least 16.7%
towards their 60% threshold (if they achieved this each month then
they would reach 60% in September)


## UDA cumulative activity data for 2021/2022

```{r echo = FALSE, warning = FALSE, fig.height=4}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data, UDAorUOA = "UDA", level = "National")
```

* This chart shows the cumulative (Year-to-date) activity
of the 6851 GDS/PDS/PDS+ contracts) measured against the
expected monthly total activity to achieve the 60% threshold by
September. The graph measures the total cumulative UDAs
performed divided by the total expected activity of the 60%
threshold.
* From April to July 4282 contracts (62%) are at least two thirds
towards delivering the 60% threshold.

## UDA delivery July-20 to July-21

```{r echo = FALSE, warning = FALSE, fig.height=4}
plot_UDA_UOA_delivery(data = UDA_scheduled_data, existing_data = slide5_UDA_delivery_historic, UDAorUOA = "UDA")
```

* This graph shows the average UDA delivery as a % of
contracted activity when each month has been scaled up to
12 months. The graph uses scheduled data to measure the
activity
* The table below shows the proportion of practices delivering
between a certain % group of contracted UDA activity from
July 2020 to July 2021 if performance for that
month is annualised. As with the graph the table uses
scheduled data.

## UOA activity data for 2021/2022

```{r echo = FALSE, warning = FALSE, fig.height=4}
plot_UDA_UOA_to_target(data = UOA_calendar_data, UDAorUOA = "UOA", level = "National")
```

* This chart shows the average monthly performance of
the 757 GDS/PDS contracts (with annual contracted UDAs of
greater than or equal to 100) measured against the minimum
activity required (16.7%) to reach the 80% threshold by September
* In the month of July 230 contracts (30%) achieved at least 16.7%
towards their 80% threshold (if they achieved this each month then
they would reach 80% in September)

## UOA cumulative activity data for 2021/2022

```{r echo = FALSE, warning = FALSE, fig.height=4}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data, UDAorUOA = "UOA", level = "National")
```

* This chart shows the cumulative (Year-to-date) average
activity of the 757 GDS/PDS contracts) measured against the
expected monthly activity to achieve the 80% threshold by
September. The graph measures the total cumulative UOAs
performed divided by the total expected activity of the 80%
threshold.
* From April to July 359 contracts (47%) are at least two thirds
towards delivering the 80% threshold

## UOA delivery July-20 to July-21

```{r echo = FALSE, warning = FALSE, fig.height=4}
plot_UDA_UOA_delivery(data = UOA_scheduled_data, existing_data = slide7_UOA_delivery_historic, UDAorUOA = "UOA")
```

* This graph shows the average UOA delivery as a % of contracted
activity when each month has been scaled up to 12 months. The
graph uses scheduled data to measure the activity. 
* The table below shows the proportion of practices delivering
between a certain % group of contracted UOA activity from July
2020 to July 2021 if performance for that month is annualised. As
with the graph the table uses scheduled data. 

## Time series of banded Courses of Treatment 2019-20 to 2021-22
```{r echo = FALSE, warning = FALSE}
plot_banded_CoT(data = UDA_scheduled_data, existing_data = slide8_banded_CoT_historic)
```

## Urgent treatment form submissions in July 2021 saw an increase from June 2021

```{r echo = FALSE, warning = FALSE, fig.height=4}
plot_urgent_form_submissions(data = UDA_scheduled_data, existing_data = slide8_banded_CoT_historic)
```

* This graph shows the number of urgent treatment forms
declared per month from April to March in both
2019/2020 and 2020/2021, and just for April to July in
2021/2022. 
* The urgent treatment form count in July 2021 was
356,885, whilst in July 2019-20 this number was
395,931, which is a 10% decrease from the pre-COVID
world. 