---
title: "Dental Data Pack"
subtitle: "`r params$region_STP_name`"
date: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  xaringan::moon_reader:
    css: [theme.css, nhsr-fonts.css]
    self_contained: true
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
params:
  level: "National"
  region_STP_name: NULL
---


```{r setup, include=FALSE}

library(tidyverse)
library(readxl)
source("../R/03 SMT_plot_functions.R")
source("../R/02 format_SMT_data.R")
#load in raw data
UDA_calendar_data <- read_excel("../data/cleaned_data_up_to_march/UDA_calendar_data.xlsx")
UOA_calendar_data <- read_excel("../data/cleaned_data_up_to_march/UOA_calendar_data.xlsx")
UDA_scheduled_data <- read_excel("../data/cleaned_data_up_to_march/UDA_scheduled_data.xlsx")
UOA_scheduled_data <- read_excel("../data/cleaned_data_up_to_march/UOA_scheduled_data.xlsx")
historical_UDA_scheduled_data <- read_excel("../data/cleaned_data_up_to_february/historical_UDA_scheduled_data.xlsx")
UDA_calendar_data <- rename(UDA_calendar_data, month = data_month)
UOA_calendar_data <- UOA_calendar_data %>%
  rename(month = data_month) %>%
  mutate(contract_number = as.numeric(contract_number),
         UOA_total = as.numeric(UOA_total)) 
    #add a region column to the data
    region_STP_lookup <- UDA_calendar_data %>%
      select(contract_number, name_or_company_name, commissioner_name, region_name) %>%
      distinct()
    
    UOA_calendar_data <- left_join(UOA_calendar_data, region_STP_lookup, by = c("contract_number", "name_or_company_name", "commissioner_name"))
UDA_scheduled_data <- rename(UDA_scheduled_data, month = data_month)
UOA_scheduled_data <- rename(UOA_scheduled_data, month = data_month)
dental_data_111 <- read_excel("../data/cleaned_data_up_to_march/dental_data_111_Mar22.xls")
prototype_contracts <- read_excel("../data/prototype_contracts.xlsx")
contractor_categories <- readRDS("../data/cleaned_data_up_to_october/contractor_categories.RDS")
UDA_delivery_calendar <- get_delivery_data_calendar(STP_lines = T, renameColumns = T)
UDA_delivery_scheduled <- get_delivery_data(STP_lines = T, renameColumns = T)
#prototype_delivery <- readRDS("~/R-Projects/SMT-Dental-Report/data/prototype_delivery.RDS")
contract_demographics <- readRDS("../data/contract_demographics.rds")
#read in unique patients
unique_patients_static <- readRDS("../data/unique_patients/unique_patients_static.rds")
unique_patients_rolling <- readRDS("../data/unique_patients/unique_patients_rolling.rds")
#evaluate chunks based on pack level
if(params$level == "National"){
  evaluate_contents_1 <- TRUE
  evaluate_contents_2 <- FALSE
  evaluate_regional <- TRUE
  evaluate_STP <- FALSE
  evaluate_111 <- TRUE
}else if(params$level == "Regional"){
  evaluate_contents_1 <- TRUE
  evaluate_contents_2 <- FALSE
  evaluate_regional <- FALSE
  evaluate_STP <- TRUE
  evaluate_111 <- FALSE
}else{
  evaluate_contents_1 <- FALSE
  evaluate_contents_2 <- TRUE
  evaluate_regional <- FALSE
  evaluate_STP <- FALSE
  evaluate_111 <- FALSE
}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#avoid standard form
options(scipen=999)

```



### Contents  

 <font size="2">
#### Dental
* Table of number of contracts by MY category [4]
* Calendar UDA activity [5]
* Calendar UDA activity by MY category [6, 7]
* Cumulative UDA delivery per quarter [8]
* Scheduled UDAs [9]
* Contract size vs delivery scatter plot [10]
* UDA delivery profile across months [11]
* Banded courses of treatment time series [18]
* Urgent treatment form submissions [19]
* 111 call volumes [20]
* 111 call volumes by disposition [21]
* Unique patients seen rolling 12 months [22]

#### Orthodontic
* Calendar UOA activity [12]
* Calendar UOA activity by MY category [13, 14]
* Cumulative UOA delivery per quarter [15]
* Scheduled UOAs [16]
* UOA delivery profile across months [17]

#### Appendix
* MY Category classification breakdown [23, 24]
* Data sources [25]

#### NOTE 
This is an interactive markdown report.  You can navigate from slide to slide by either clicking the mouse on the screen or by using the cursor keys.  **Press ? for help.** 
Some pages have selection buttons across regions, click on the region in order to explore the data for that area.  
This format also works on mobile devices in browser with no further software required, but has been optimised for 16:9 screen ratio.

---

### Calendar and scheduled data

<font size="2">
#### Calendar data explanation

* Slides 5-9 and 13-17 are based on calendar month data
* Calendar data is based on courses of treatment completed within an entire month, for example 1st February to 28th Feb
* For calendar data, if a COT was completed in February but not declared till March, that activity would still be registered as
occurring in February.
* This means that graphs using calendar data may change for historical months as more COTs are registered.
* The activity % is now based on total number of UDA/UOAs delivered as a % of total contracted UDA/UOAs per quarter.


#### Scheduled data explanation
* Slides 10-12 and 18-21 are based on scheduled data
* The scheduling time period is usually between the 20th of one month and the 20th of the next month i.e., 21st April to the
19th May. That means that any Mandatory contract COT completed after this period will not be included in the May
scheduled data. However, if for example a COT was completed on May 1st, but reported to the BSA after the end of the
reporting period (April 21st – May 19th), that activity would go into the following scheduled period. As a result, the
scheduling period can be considered fixed.
* N.B.Scheduled data for April is from 1st April - 21st April. This has been taken into account when scaling up to annual delivery.

---

```{css, echo=F}
    /* Table width = 100% max-width */

    .remark-slide table{
        width: 100%;
    }

    /* Change the background color to white for shaded rows (even rows) */

    .remark-slide thead, .remark-slide tr:nth-child(2n) {
        background-color: white;
    }
```

### Number of contracts by Mid-Year (MY) category 
(see appendix for category descriptions)

```{r xaringan-panelset-contracts, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table11, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "National", region_STP_name = NULL), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table21, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "National", region_STP_name = NULL), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


]
.panel[.panel-name[South East]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table12, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "Regional", region_STP_name = "South East"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table22, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "Regional", region_STP_name = "South East"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



]
.panel[.panel-name[South West]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table13, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "Regional", region_STP_name = "South West"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table23, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "Regional", region_STP_name = "South West"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



]
.panel[.panel-name[North West]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table14, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "Regional", region_STP_name = "North West"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table24, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "Regional", region_STP_name = "North West"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



]
.panel[.panel-name[North East and Yorkshire]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table15, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "Regional", region_STP_name = "North East and Yorkshire"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table25, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "Regional", region_STP_name = "North East and Yorkshire"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



]
.panel[.panel-name[London]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table16, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "Regional", region_STP_name = "London"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table26, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "Regional", region_STP_name = "London"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


]
.panel[.panel-name[Midlands]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table17, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "Regional", region_STP_name = "Midlands"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table27, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "Regional", region_STP_name = "Midlands"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



]
.panel[.panel-name[East of England]

#### Including prototypes and contracts with annual contracted UDA < 100
```{r table18, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = F, level = "Regional", region_STP_name = "East of England"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

#### Excluding prototypes and contracts with annual contracted UDA < 100
```{r table28, echo = FALSE, warning = FALSE, message = FALSE}
knitr::kable(table_number_cat_contracts(remove_prototypes = T, level = "Regional", region_STP_name = "East of England"), format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



]
]


---

### UDA Activity Data

```{r xaringan-panelset-UDA-activity, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r UDA_activity_Calendar1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "National", region_STP_name = NULL)`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[South East]
```{r UDA_activity_Calendar2, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South East",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "South East")`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[South West]
```{r UDA_activity_Calendar3, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South West",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "South West")`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[North West]
```{r UDA_activity_Calendar4, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North West",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "North West")`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[North East and Yorkshire]
```{r UDA_activity_Calendar5, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "North East and Yorkshire")`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[London]
```{r UDA_activity_Calendar6, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "London",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "London")`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[Midlands]
```{r UDA_activity_Calendar7, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "Midlands",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "Midlands")`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[East of England]
```{r UDA_activity_Calendar8, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data, 
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Region",
                                  region_STP_name = "East of England",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "Regional", region_STP_name = "East of England")`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar and 95% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally higher to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported. 

]
.panel[.panel-name[All]
```{r UDA_activity_Calendar9, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = params$level,
                                  region_STP_name = params$region_STP_name,
                                  remove_prototypes = T,
                                  regional_lines = T,
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

]
]

---

### UDA activity data by MY Category
#### Prototypes and contracts with annual contracted UDAs < 100 included

```{r xaringan-panelset-UDA-activity-My-CAT, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South East",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South West",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North West",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "London",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "Midlands",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "East of England",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
]


---

### UDA activity data by MY Category
#### Prototypes and contracts with annual contracted UDAs < 100 excluded

```{r xaringan-panelset-UDA-activity-My-CAT2, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South East",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South West",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North West",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "London",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "Midlands",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UDA_calendar_data,
                                  scheduled_data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "East of England",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

]
]

---

### UDA cumulative activity data

```{r xaringan-panelset-UDA_cumulative_activity, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL)
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "National", region_STP_name = NULL)`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")` 
**`r get_Q4_num_contracts_on_target(level = "National", region_STP_name = NULL)`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "National", region_STP_name = NULL)*100/get_num_contracts(level = "National", region_STP_name = NULL))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South East")
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "Regional", region_STP_name = "South East")`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "South East")`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "South East")*100/get_num_contracts(level = "Regional", region_STP_name = "South East"))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.


]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South West")
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "Regional", region_STP_name = "South West")`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "South West")`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "South West")*100/get_num_contracts(level = "Regional", region_STP_name = "South West"))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.


]
.panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North West")
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "Regional", region_STP_name = "North West")`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "North West")`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "North West")*100/get_num_contracts(level = "Regional", region_STP_name = "North West"))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.


]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire")
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "Regional", region_STP_name = "North East and Yorkshire")`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "North East and Yorkshire")`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "North East and Yorkshire")*100/get_num_contracts(level = "Regional", region_STP_name = "North East and Yorkshire"))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.


]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "London")
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "Regional", region_STP_name = "London")`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "London")`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "London")*100/get_num_contracts(level = "Regional", region_STP_name = "London"))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "Midlands")
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "Regional", region_STP_name = "Midlands")`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "Midlands")`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "Midlands")*100/get_num_contracts(level = "Regional", region_STP_name = "Midlands"))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.


]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_calendar_data,
                                  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "East of England")
```

* This graph shows the cumulative activity by quarter of the 
**`r get_num_contracts(level = "Regional", region_STP_name = "East of England")`** 
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (95% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "East of England")`**
contracts (
**`r round(get_Q4_num_contracts_on_target(level = "Regional", region_STP_name = "East of England")*100/get_num_contracts(level = "Regional", region_STP_name = "East of England"))` %**
) have delivered the required UDAs or more to be on track towards the Q1 threshold (95%) by the end of June 2022.


]
]

---

### Scheduled UDAs

```{r xaringan-panelset-UDA_activity_scheduled, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL)
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.

]
.panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South East")
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.


]
.panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "South West")
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.


]
.panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North West")
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.


]
.panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire")
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.


]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "London")
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.

]
.panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "Midlands")
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.


]
.panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "Regional",
                                  region_STP_name = "East of England")
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.


]
]


---

### Contract size to delivery comparison

```{r xaringan-panelset-contract_size, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "National",
                                                 region_STP_name = NULL)
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "National", region_STP_name = NULL, get_num_above = 0.95)[1]`**
(
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "National", region_STP_name = NULL, get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "National", region_STP_name = NULL))`** 
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "National", region_STP_name = NULL, get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "National", region_STP_name = NULL, get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "National", region_STP_name = NULL, get_num_above = 1)[2]`** 
UDAs.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "Regional",
                                                 region_STP_name = "South East")
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South East", get_num_above = 0.95)[1]`**
( 
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South East", get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "Regional", region_STP_name = "South East"))`**  
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South East", get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South East", get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South East", get_num_above = 1)[2]`** 
UDAs.


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "Regional",
                                                 region_STP_name = "South West")
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South West", get_num_above = 0.95)[1]`**
( 
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South West", get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "Regional", region_STP_name = "South West"))`**  
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South West", get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South West", get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "South West", get_num_above = 1)[2]`** 
UDAs.


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "Regional",
                                                 region_STP_name = "North West")
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North West", get_num_above = 0.95)[1]`**
( 
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North West", get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "Regional", region_STP_name = "North West"))`**  
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North West", get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North West", get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North West", get_num_above = 1)[2]`** 
UDAs.


 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "Regional",
                                                 region_STP_name = "North East and Yorkshire")
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North East and Yorkshire", get_num_above = 0.95)[1]`**
( 
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North East and Yorkshire", get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "Regional", region_STP_name = "North East and Yorkshire"))`**  
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North East and Yorkshire", get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North East and Yorkshire", get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "North East and Yorkshire", get_num_above = 1)[2]`** 
UDAs.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "Regional",
                                                 region_STP_name = "London")
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "London", get_num_above = 0.95)[1]`**
( 
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "London", get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "Regional", region_STP_name = "London"))`**  
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "London", get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "London", get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "London", get_num_above = 1)[2]`** 
UDAs.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "Regional",
                                                 region_STP_name = "Midlands")
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "Midlands", get_num_above = 0.95)[1]`**
( 
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "Midlands", get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "Regional", region_STP_name = "Midlands"))`**  
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "Midlands", get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "Midlands", get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "Midlands", get_num_above = 1)[2]`** 
UDAs.


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_delivery_vs_contract_size_scatter_corporate(data = UDA_scheduled_data,
                                                 demographics_data = contract_demographics,
                                                 remove_prototypes = T,
                                                 plot_month = NULL,
                                                 UDAorUOA = "UDA",
                                                 level = "Regional",
                                                 region_STP_name = "East of England")
```

* The scatter plot shows the relationship between contract size and delivery for the current month.
* The number of contracts delivering above 95% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "East of England", get_num_above = 0.95)[1]`**
( 
**`r round(as.numeric(plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "East of England", get_num_above = 0.95)[1]) *100 / get_num_contracts(level = "Regional", region_STP_name = "East of England"))`**  
% of contracts),
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "East of England", get_num_above = 0.95)[2]`** 
UDAs.
* The number of contracts delivering above 100% contracted value for this month is 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "East of England", get_num_above = 1)[1]`**,
with a mean contract size of 
**`r plot_delivery_vs_contract_size_scatter_corporate(level = "Regional", region_STP_name = "East of England", get_num_above = 1)[2]`** 
UDAs.


 ]
 ]


---

### UDA delivery profile

```{r xaringan-panelset-UDA_delivery_profile, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "National",
                          region_STP_name = NULL)
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "Regional",
                          region_STP_name = "South East")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "Regional",
                          region_STP_name = "South West")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "Regional",
                          region_STP_name = "North West")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.


 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "Regional",
                          region_STP_name = "North East and Yorkshire")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "Regional",
                          region_STP_name = "London")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "Regional",
                          region_STP_name = "Midlands")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          calendar_data = UDA_calendar_data,
                          UDAorUOA = "UDA",
                          level = "Regional",
                          region_STP_name = "East of England")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. This uses scheduled data.


 ]
 ]

---

### UOA activity data


```{r xaringan-panelset-UOA_activity, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "National", region_STP_name = NULL)`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South East",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "South East")`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South West",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "South West")`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North West",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "North West")`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.


 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "North East and Yorkshire")`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "London",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "London")`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "Midlands",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "Midlands")`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data, 
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "East of England",
                                  remove_prototypes = T,
                                  regional_lines = F, 
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_calendar_data, remove_prototypes = T, scheduled_data = UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "East of England")`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).
* N.B. Previous month's delivery may be marginally different to what was reported last month
due to the nature of calendar data (see slide 3). This month's figure is likely to be under-reported.


 ]
  .panel[.panel-name[All]
```{r UOA_activity_regional, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, eval=evaluate_regional}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = params$level,
                                  region_STP_name = params$region_STP_name,
                                  remove_prototypes = T,
                                  regional_lines = T,
                                  STP_lines = F,
                                  cat_lines = F,
                                  plot_chart = T)
```


 ]
 ]


---


### UOA activity data by MY Category
#### Prototypes and contracts with annual contracted UDAs < 100 included

```{r xaringan-panelset-UOA_MY_CAT, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South East",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South West",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```



 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North West",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```



 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "London",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "Midlands",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "East of England",
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

 ]
 ]

---

### UOA activity data by MY Category
#### Prototypes and contracts with annual contracted UDAs < 100 excluded

```{r xaringan-panelset-UOA_MY_CAT2, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South East",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South West",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North West",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "London",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "Midlands",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_calendar(data = UOA_calendar_data,
                                  scheduled_data = UOA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "East of England",
                                  remove_prototypes = T,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plot_chart = T)
```

 ]
 ]
 
---

### UOA cumulative activity data

```{r xaringan-panelset-UOA_cumulative, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL)
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "National", region_STP_name = NULL)`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "National", region_STP_name = NULL)`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "National", region_STP_name = NULL)*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "National", region_STP_name = NULL))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South East")
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "South East")`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "South East")`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "South East")*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "South East"))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South West")
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "South West")`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "South West")`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "South West")*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "South West"))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North West")
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "North West")`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "North West")`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "North West")*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "North West"))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.

 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire")
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "North East and Yorkshire")`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "North East and Yorkshire")`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "North East and Yorkshire")*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "North East and Yorkshire"))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "London")
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "London")`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "London")`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "London")*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "London"))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "Midlands")
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "Midlands")`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "Midlands")`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "Midlands")*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "Midlands"))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_calendar_data,
                                  UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "East of England")
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "East of England")`**
GDS/PDS contracts) measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::month(1), "%B")`  
**`r get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "East of England")`** 
contracts (
**`r round(get_Q4_num_contracts_on_target(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, UDAorUOA = "UOA", level = "Regional", region_STP_name = "East of England")*100/get_num_contracts(UOA_calendar_data, remove_prototypes = T, UOA_scheduled_data, "UOA", level = "Regional", region_STP_name = "East of England"))` %**
) have delivered the required UOAs or more to be on track towards the Q1 threshold (100%) by the end of June 2022.


 ]
 ]
 
---

### UOA scheduled delivery

```{r xaringan-panelset-UOA_activity_scheduled, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL)
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South East")
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "South West")
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North West")
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.


 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "North East and Yorkshire")
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "London")
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "Midlands")
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data,
                      UDAorUOA = "UOA",
                                  level = "Regional",
                                  region_STP_name = "East of England")
```

* This graph shows the monthly percentage of usual annual contracted UOAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UOAs submitted" in each month rather than delivered.


 ]
 ]
 
---

### UOA delivery profile

```{r xaringan-panelset-UOA_delivery_profile, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "National",
                          region_STP_name = NULL)
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = "South East")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = "South West")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = "North West")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.

 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = "North East and Yorkshire")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = "London")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = "Midlands")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          calendar_data = UOA_calendar_data,
                          UDAorUOA = "UOA",
                          level = "Regional",
                          region_STP_name = "East of England")
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.


 ]
 ]
 

---

### Time series of banded Courses of Treatment

```{r xaringan-panelset-CoTs, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "National",
                region_STP_name = NULL)
```


 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "South East")
```

 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "South West")
```

 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "North West")
```

 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "North East and Yorkshire")
```

 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "London")
```

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "Midlands")
```


 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, , fig.width=14, fig.height=5}
plot_banded_CoT(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "East of England")
```

 ]
 ]
 
---

### Urgent treatment form submissions

```{r xaringan-panelset-Urgent-forms, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "National",
                region_STP_name = NULL)
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "National", region_STP_name = NULL)`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "National", region_STP_name = NULL)`**
, which is a 
**`r round((get_num_urgent_forms(level = "National", region_STP_name = NULL) - get_num_urgent_forms_2019(level = "National", region_STP_name = NULL)) *100 / get_num_urgent_forms_2019(level = "National", region_STP_name = NULL))` %** 
change from the pre-COVID world.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "South East")
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "Regional", region_STP_name = "South East")`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "Regional", region_STP_name = "South East")`**
, which is a 
**`r round((get_num_urgent_forms(level = "Regional", region_STP_name = "South East") - get_num_urgent_forms_2019(level = "Regional", region_STP_name = "South East")) *100 / get_num_urgent_forms_2019(level = "Regional", region_STP_name = "South East"))` %** 
change from the pre-COVID world.


 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "South West")
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "Regional", region_STP_name = "South West")`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "Regional", region_STP_name = "South West")`**
, which is a 
**`r round((get_num_urgent_forms(level = "Regional", region_STP_name = "South West") - get_num_urgent_forms_2019(level = "Regional", region_STP_name = "South West")) *100 / get_num_urgent_forms_2019(level = "Regional", region_STP_name = "South West"))` %** 
change from the pre-COVID world.


 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "North West")
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "Regional", region_STP_name = "North West")`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "Regional", region_STP_name = "North West")`**
, which is a 
**`r round((get_num_urgent_forms(level = "Regional", region_STP_name = "North West") - get_num_urgent_forms_2019(level = "Regional", region_STP_name = "North West")) *100 / get_num_urgent_forms_2019(level = "Regional", region_STP_name = "North West"))` %** 
change from the pre-COVID world.


 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "North East and Yorkshire")
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "Regional", region_STP_name = "North East and Yorkshire")`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "Regional", region_STP_name = "North East and Yorkshire")`**
, which is a 
**`r round((get_num_urgent_forms(level = "Regional", region_STP_name = "North East and Yorkshire") - get_num_urgent_forms_2019(level = "Regional", region_STP_name = "North East and Yorkshire")) *100 / get_num_urgent_forms_2019(level = "Regional", region_STP_name = "North East and Yorkshire"))` %** 
change from the pre-COVID world.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "London")
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "Regional", region_STP_name = "London")`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "Regional", region_STP_name = "London")`**
, which is a 
**`r round((get_num_urgent_forms(level = "Regional", region_STP_name = "London") - get_num_urgent_forms_2019(level = "Regional", region_STP_name = "London")) *100 / get_num_urgent_forms_2019(level = "Regional", region_STP_name = "London"))` %** 
change from the pre-COVID world.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "Midlands")
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "Regional", region_STP_name = "Midlands")`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "Regional", region_STP_name = "Midlands")`**
, which is a 
**`r round((get_num_urgent_forms(level = "Regional", region_STP_name = "Midlands") - get_num_urgent_forms_2019(level = "Regional", region_STP_name = "Midlands")) *100 / get_num_urgent_forms_2019(level = "Regional", region_STP_name = "Midlands"))` %** 
change from the pre-COVID world.

 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_urgent_form_submissions(data = UDA_scheduled_data,
                calendar_data = UDA_calendar_data,
                historic_data = historical_UDA_scheduled_data,
                level = "Regional",
                region_STP_name = "East of England")
```

* This graph shows the number of urgent treatment forms
declared per month across financial years.
* The urgent treatment form count in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2021** 
was
**`r get_num_urgent_forms(level = "Regional", region_STP_name = "East of England")`**
, whilst in 
**`r format(Sys.Date() - lubridate::weeks(4), "%B")` 2019** 
this number was
**`r get_num_urgent_forms_2019(level = "Regional", region_STP_name = "East of England")`**
, which is a 
**`r round((get_num_urgent_forms(level = "Regional", region_STP_name = "East of England") - get_num_urgent_forms_2019(level = "Regional", region_STP_name = "East of England")) *100 / get_num_urgent_forms_2019(level = "Regional", region_STP_name = "East of England"))` %** 
change from the pre-COVID world.

 ]
 ]
 

---

### 111 dental related call volumes

```{r 111_volumes, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, eval=evaluate_111}
plot_111_referrals()
```


---

### 111 dental related call volumes by disposition

```{r 111_volumes_breakdown, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, eval=evaluate_111}
plot_breakdown_111_referrals()
```

---

### Unique dental patients seen

```{r xaringan-panelset-Unique-patients, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "National",
                                     region_STP_name = NULL,
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "National",region_STP_name = NULL, plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.

 ]
 .panel[.panel-name[South East]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "Regional",
                                     region_STP_name = "South East",
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "Regional",region_STP_name = "South East", plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.

 ]
 .panel[.panel-name[South West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "Regional",
                                     region_STP_name = "South West",
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "Regional",region_STP_name = "South West", plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.

 ]
 .panel[.panel-name[North West]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "Regional",
                                     region_STP_name = "North West",
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "Regional",region_STP_name = "North West", plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.

 ]
 .panel[.panel-name[North East and Yorkshire]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "Regional",
                                     region_STP_name = "North East and Yorkshire",
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "Regional",region_STP_name = "North East and Yorkshire", plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.


 ]
.panel[.panel-name[London]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "Regional",
                                     region_STP_name = "London",
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "Regional",region_STP_name = "London", plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.

 ]
 .panel[.panel-name[Midlands]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "Regional",
                                     region_STP_name = "Midlands",
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "Regional",region_STP_name = "Midlands", plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.

 ]
 .panel[.panel-name[East of England]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_unique_patients_rolling(data = unique_patients_rolling,
                                     calendar_data = UDA_calendar_data,
                                     scheduled_data = UDA_scheduled_data,
                                     level = "Regional",
                                     region_STP_name = "East of England",
                                     plotChart = TRUE,
                                     remove_prototypes = TRUE)
```

* The number of unique patients seen in the last 12 months is currently around 
**`r plot_unique_patients_rolling(level = "Regional",region_STP_name = "East of England", plotChart = F,remove_prototypes = T, get_perc = T)` %**
of pre-pandemic levels.

 ]
 ]
 
---

### Appendix
#### MY Category classification breakdown:

 <font size="2">
* Cat 1
  + Details in CoMPASS Correct
* Cat 2
  + Carry Forward - Other
  + Flexibly Commissioned Contract
  + Force majeure accepted
  + Force majeure o/s
  + In-year incorporation/merge (Parent contract - letter will be sent)
  + Incomplete OOH/other access services
  + Late subs processed
  + Mixed / CoT Contract
  + Non-recurring activity
  + Open in-year
  + Other
  + Request to re-base
  + Review Carry Forward
  + Sub Contracts (Parent contract - letter will be sent)
  + UDA Value below £15.00
  + UDA Value exceeds £49.99
  + UDC
  + UOA Value exceeds £75.00
  + Closed in-year
  + Incomplete service line entries


---

 <font size="2">
* Cat 3
  + CDS
  + Closed in year
  + Contract End Date before 01/04/2020
  + Contract End Date before 01/04/2021
  + Contract End Date before 01/04/2022
  + DCO req to resolve locally
  + Domiciliary/ Sedation
  + IMOS/MOS
  + In-year incorporation/merge (Child contract - letter will not be sent)
  + Incomplete OOH/other access services
  + Known performance/contract issues
  + No Contracted activity
  + No Contracted value
  + Not paid by the NHSBSA
  + Open in year
  + Other
  + Other - Please state why
  + Other Advanced/Additional Services
  + PDS Plus
  + Prison
  + Sub Contracts (Child contract - letter will not be sent)
* Cat 4
  + Dental Contract Reform

---

#### Data sources

 <font size="2">
* BSA calendar and scheduled UDA data downloaded from the "NHS England Central Dashboard" on eDEN. This data is downloaded monthly and put on the NCDR. 
* Tables are:
  + [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UDA_calendar]
  + [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UDA_scheduled]
  + [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UOA_calendar]
  + [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UOA_scheduled]
* A list of prototype contracts are also available in:
  + [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[prototype_contracts]
* Tables of UDA delivery on STP level in calendar and scheduled format available in:
  + [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UDA_delivery_calendar]
  + [NHSE_Sandbox_PrimaryCareNHSContracts].[Dental].[UDA_delivery_scheduled]

* 111 data comes from the pathways tool which is received monthly by email.




<!--  ```{r xaringan-panelset-UDA-activity, echo=FALSE} -->
<!--  xaringanExtra::use_panelset() -->
<!--  ``` -->
<!--   <font size="2"> -->
<!--  .panelset[ -->

<!--  .panel[.panel-name[National] -->


<!--  ] -->
<!--  .panel[.panel-name[South East] -->



<!--  ] -->
<!--  .panel[.panel-name[South West] -->



<!--  ] -->
<!--  .panel[.panel-name[North West] -->



<!--  ] -->
<!--  .panel[.panel-name[North East and Yorkshire] -->



<!--  ] -->
<!-- .panel[.panel-name[London] -->


<!--  ] -->
<!--  .panel[.panel-name[Midlands] -->



<!--  ] -->
<!--  .panel[.panel-name[East of England] -->



<!--  ] -->
<!--  ] -->


<!-- --- -->






<!-- --- -->
<!-- ### Download data: Pharmacy sign-up -->

<!-- ```{r xaringan-panelset-data-sign-ups, echo=FALSE} -->
<!-- xaringanExtra::use_panelset() -->
<!-- ``` -->
<!--  <font size="1"> -->
<!-- .panelset[ -->
<!-- .panel[.panel-name[Pharmacy Sign-up data] -->
<!-- ```{r echo=FALSE, results='asis',warning=FALSE, fig.width=3, fig.height=3} -->

<!-- DT::datatable(CVDclaims,rownames=FALSE,  extensions = 'Buttons', options = list(dom='Bt', buttons = c('excel'), -->
<!--   bPaginate = FALSE, pageLength=50, columnDefs = list(list(className = 'dt-left', targets = 0:4)),searching=FALSE,scrollY ='500px'))%>% -->
<!--   DT::formatStyle(columns = c(1, 2, 3, 4, 5), fontSize = '130%') -->
<!-- ``` -->
<!-- ] -->
<!-- ] -->