---
title: "Dental Data Pack"
subtitle: "National"
date: "`r paste(format(Sys.time(), '%B, %Y'), ' - Reporting up to end of', format(Sys.Date() - lubridate::weeks(4), '%B, %Y'))`"
output:
  xaringan::moon_reader:
    css: [theme.css, nhsr-fonts.css]
    self_contained: true
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}

library(tidyverse)
library(readxl)
library(DBI)
library(odbc)
library(reactable) #make sure you have the latest version by doing install.packages("reactable")
library(downloadthis)
library(lubridate)

#source in all file from plot folder
for (f in list.files(path = "../R/03 plot_functions/", pattern="*.R$")) {
    source(paste0("../R/03 plot_functions/", f))
}

for (f in list.files(path = "../R/02 format_data_functions/", pattern="*.R$")) {
    source(paste0("../R/02 format_data_functions/", f))
}


#pull data from NCDR
UDA_calendar_data <- pull_UDA_calendar_data()
UOA_calendar_data <- pull_UOA_calendar_data()
UDA_scheduled_data <- pull_UDA_scheduled_data()
UOA_scheduled_data <- pull_UOA_scheduled_data()
payments_to_dentists <- pull_payments_to_dentist()

historical_UDA_scheduled_data <- pull_UDA_scheduled_historical_data()
historical_UDA_scheduled_data <- rename(historical_UDA_scheduled_data, month = data_month)

#change column names and add regions
UDA_calendar_data <- rename(UDA_calendar_data, month = data_month)
UOA_calendar_data <- UOA_calendar_data %>%
  rename(month = data_month) %>%
  mutate(contract_number = as.numeric(contract_number),
         UOA_total = as.numeric(UOA_total)) 

    
# UOA_calendar_data <- left_join( region_STP_lookup, by = c("contract_number", "name_or_company_name", "commissioner_name"))
UDA_scheduled_data <- rename(UDA_scheduled_data, month = data_month)
UOA_scheduled_data <- rename(UOA_scheduled_data, month = data_month)

UDA_scheduled_data <- mutate(UDA_scheduled_data, month = as.Date(month))
UOA_scheduled_data <- mutate(UOA_scheduled_data, month = as.Date(month))

#sort out STP ICB changes
STP_ICB_lookup_codes <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/STP_ICB_lookup_codes.xlsx")

#Read local 111 file
dental_data_111 <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/111_pathways_data/dental_data_111.xlsx")

#############still to fix
prototype_contracts <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/prototype_contracts.xlsx")
contractor_categories <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/contractor_categories.xlsx")
contractor_categories <- contractor_categories %>%
  mutate(contract_number = as.numeric(contract_number))
contract_demographics <- readRDS("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/contract_demographics.rds")

#read in unique patients
#unique_patients_rolling <- readRDS("../data/unique_patients/unique_patients_rolling.rds")
unique_patients_rolling <- pull_unique_patients_data()

#read in recalls 
dental_recalls_STP_2018_22 <- readRDS("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/dental_recalls_STP_2018_22.rds")

#read in CDS data
CDS_data <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/CDS/CDS_data.xlsx")
CDS_data <- clean_CDS_data_colnames(CDS_data)

#read in hand backs data
contract_handbacks <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/contract_handbacks.xlsx")

#read in and clean complaints data
Dental_Access_Complaints_Data_June_22 <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/complaints/Dental Access Complaints Data June 22.xlsx")
dental_complaints <- clean_complaints_data(Dental_Access_Complaints_Data_June_22)

#UDA value data
UDA_values <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/UDA_values.xlsx")
UDA_UOA_value_data <- pull_UDA_UOA_value()

#Pull patient charge data
patient_exemption_data <- pull_patient_exemption_data()
patient_exemption_data <- clean_patient_exemption_data()

#pull health inequalities data
health_inequalities_data <- pull_health_inequalities()

missing_contracts_data <- read_excel("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/data_for_monthly_report/missing_contract_details.xlsx")

#DCP_data <- read.csv("N:/_Everyone/Primary Care Group/SMT_Dental DENT 2022_23-008/DCP_data/DPC_v1_Oct_2022.csv") 
DCP_data <- pull_dcp_data()

BPE_data <- pull_BPE_data()

band2_split_data <- pull_band2_split_data()

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#avoid standard form
options(scipen=999)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)

```


name: short-uda-activity

### UDA Activity Data

```{r xaringan-panelset-UDA-activity, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r UDA_activity_Calendar1, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery(data = UDA_scheduled_data, 
                                  
                                  historic_data = historical_UDA_scheduled_data,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = TRUE, 
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  include_historic = FALSE)
```

* This graph shows the average monthly performance of the **`r get_num_contracts(level = "National", region_STP_name = NULL)`** GDS/PDS/PDS+ contracts scaled up by 12 months measured against the delivery thresholds (60% for Apr-Sep 21, 65% for Oct-Dec, 85% for Jan-Mar, 95% for Apr-Jun 22 and 100% going forward).


]

.panel[.panel-name[Regions]
```{r UDA_activity_Calendar9, echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5, fig.align='center'}
plot_UDA_UOA_delivery_all_regions(data = UDA_scheduled_data, 
                                              
                                              historic_data = historical_UDA_scheduled_data,
                                              UDAorUOA = "UDA",
                                              level = "National",
                                              region_STP_name = NULL,
                                              remove_prototypes = TRUE, 
                                              plotChart = TRUE, 
                                              all_regions_and_STPs = FALSE,
                                   include_historic = F)
```

]
]

---

name: short-uda-activity-my-cat

### UDA activity data by MY Category
#### Prototypes and contracts with annual contracted UDAs < 100 included

```{r xaringan-panelset-UDA-activity-My-CAT, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_MY_cat(
                             data = UDA_scheduled_data,
                                  contractor_cats = contractor_categories,
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = F,
                                  regional_lines = F,
                                  STP_lines = F,
                                  cat_lines = T,
                                  plotChart = T)
```

]
]

---

name: cumulative-udas

### UDA cumulative activity data

```{r xaringan-panelset-UDA_cumulative_activity, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UDA_scheduled_data,
                                  
                                  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL)
```

* This graph shows the cumulative activity by quarter of the
**`r get_num_contracts(level = "National", region_STP_name = NULL)`**
GDS/PDS/PDS+
contracts measured against the expected monthly total activity to achieve the quarterly thresholds (100% for Jan-Mar 23).
* From the start of April to the end of `r format(Sys.Date() - lubridate::weeks(4), "%B")`
**`r get_quarterly_num_contracts_on_target(level = "National", region_STP_name = NULL)`**
contracts (
**`r round(get_quarterly_num_contracts_on_target(level = "National", region_STP_name = NULL)*100/get_num_contracts(level = "National", region_STP_name = NULL))` %**
) have delivered the required UDAs or more to be on track towards the Q4 threshold (100%) by the end of March 2023.

]
]

---

name: historic-udas

### Historic UDA delivery

```{r xaringan-panelset-UDA_activity_scheduled, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

.panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UDA_scheduled_data,  UDAorUOA = "UDA",
                                  level = "National",
                                  region_STP_name = NULL)
```

* This graph shows the monthly percentage of usual annual contracted UDAs scaled up to 12 months (18 months for April) submitted. The graph uses scheduled data to measure the
activity which is fixed. This may be thought of as "UDAs submitted" in each month rather than delivered.

]
]

---

name: uda-delivery-profile

### UDA delivery profile

```{r xaringan-panelset-UDA_delivery_profile, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UDA_scheduled_data,
                          
                          UDAorUOA = "UDA",
                          level = "National",
                          region_STP_name = NULL,
                          include_historic = FALSE)
```

 ]
 ]
 
 This graph shows the proportion of practices delivering
between a certain % group of contracted UDA activity if performance for that
month is annualised. Improvement would be seen as the distribution moving towards the right, as more contracts deliver closer to 100% of their contracted UDAs.


---

name: uoa-activity

### UOA activity data


```{r xaringan-panelset-UOA_activity, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery(data = UOA_scheduled_data, 
                                  
                                  historic_data = historical_UDA_scheduled_data,
                                  UDAorUOA = "UOA",
                                  level = "National",
                                  region_STP_name = NULL,
                                  remove_prototypes = TRUE, 
                                  plotChart = TRUE, 
                                  all_regions_and_STPs = FALSE,
                                  include_historic = FALSE)
```

* This graph shows the average monthly performance of the
**`r get_num_contracts(data = UOA_scheduled_data, remove_prototypes = T,  UDAorUOA = "UOA", level = "National", region_STP_name = NULL)`**
GDS/PDS contracts scaled up by 12 months measured against the delivery thresholds (80% for Apr-Sep 21, 85% for Oct-Dec, 90% for Jan-Mar, 100% for Apr-Jun 22).

 ]
]

---

name: cumulative-uoas

### UOA cumulative activity data

```{r xaringan-panelset-UOA_cumulative, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_cumulative_UDA_UOA_to_target(data = UOA_scheduled_data, 
                                              
                                              UDAorUOA = "UOA", 
                                              level = "National",
                                              region_STP_name = NULL,
                                              plotChart = TRUE,
                                              all_regions_and_STPs = FALSE,
                                              remove_prototypes = TRUE)
```

* This graph shows the cumulative activity by quarter of the **`r get_num_contracts(UOA_scheduled_data, remove_prototypes = T, UDAorUOA = "UOA", level = "National", region_STP_name = NULL)`**
GDS/PDS contracts measured against the
expected monthly total activity to achieve the quarterly thresholds (100% for Apr-Jun 22).
* From the start of April to the end of `r format(Sys.Date() - lubridate::weeks(4), "%B")`
**`r get_quarterly_num_contracts_on_target(UOA_scheduled_data, remove_prototypes = T, UDAorUOA = "UOA", level = "National", region_STP_name = NULL)`**
contracts (
**`r round(get_quarterly_num_contracts_on_target(UOA_scheduled_data, remove_prototypes = T, UDAorUOA = "UOA", level = "National", region_STP_name = NULL)*100/get_num_contracts(UOA_scheduled_data, remove_prototypes = T, UDAorUOA = "UOA", level = "National", region_STP_name = NULL))` %**
) have delivered the required UOAs or more to be on track towards the Q4 threshold (100%) by the end of March 2023.

 ]
 ]

---

name: uoa-delivery-profile

### UOA delivery profile

```{r xaringan-panelset-UOA_delivery_profile, echo=FALSE}
xaringanExtra::use_panelset()
```
 <font size="2">
.panelset[

 .panel[.panel-name[National]
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.width=14, fig.height=5}
plot_UDA_UOA_delivery_profile(data = UOA_scheduled_data,
                          
                          UDAorUOA = "UOA",
                          level = "National",
                          region_STP_name = NULL)
```

* The graph shows the proportion of practices delivering
between a certain % group of contracted UOA activity if performance for that
month is annualised.
This uses scheduled data.

 ]
 ]

